---
title: "Bio-Imaging Development Strategies"
author: "Sangho Lee"
date: ' '
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: sentence
---

```{css, echo=FALSE}
body {
  font-family: 'Verdana', sans-serif;
}

#footer {
position: fixed;
left: 0;
bottom: 0;
width: 100%;
background-color: #f2f2f2; /* You can change the background color */
  color: black; /* Text color */
  text-align: center;
padding: 10px 0;
font-size: 1.2em;
}

```

------------------------------------------------------------------------

------------------------------------------------------------------------

# **Case Summary**

<br><br>

**Note:** *This summary offers a creatively rephrased perspective of the
original case study. It aims to provide an engaging and understandable
narrative.*

# **Bio-Imaging's Development Dilemma: Choosing the Path to Innovation** <br><br>

<br>

**Part 1**<br>
Bio-Imaging Inc. finds itself at a pivotal point with their advanced 3D brain imaging technology. Medtech Corporation steps in, offering a solid $150K for their software. It's a tempting offer that guarantees immediate financial gain. <br><br>

**Part 2**<br>
If their product is a success, they're faced with new options. One is to apply for the SBIR grant, which could bring in $300,000 without diluting their ownership. The other is to accept a $1 million offer from Nugrowth Development, but this would mean parting with 80% of future profits. The financial outcomes vary significantly: the SBIR route could lead to a high profit of $2.8 million, a medium gain of $300K, or a potential loss of $200K. The Nugrowth deal offers its own set of possibilities: a high profit of $1.8 million, a comfortable $400K, or a loss of $200K.<br><br>

**Part 3**<br>
If their 3D project not succeeded, Bio-Imaging would have had to make a tough call between abandoning their project or pivoting to their 2D technology and hoping for a SBIR grant. This alternate route comes with a 20% chance of success, potentially leading to a high profit of $1.2 million, or a loss of $300K.<br><br>

**Part 4**<br>
Each decision point for Bio-Imaging is a complex balance of potential high, medium, and low profits against significant risks. Their financial path is uncertain yet full of potential, with each choice critically shaping their role in the competitive medical technology market.
<br><br>

**Part 5**<br>
Bio-Imaging's journey is akin to navigating the challenging waters of business innovation. Their story is one of making calculated, strategic decisions in the dynamic and high-stakes environment of medical technology. Each decision not only impacts their financial standing but also reflects their commitment to pushing the boundaries of medical innovation.
<br><br>


**Part 6**<br>
***Medtech:***
<br>
Medtech Corporation offers a straightforward deal: $150K for Bio-Imaging's software. It's a clear path to immediate financial gain but at the cost of relinquishing future opportunities and advancements in their technology.
<br><br>
***SBIR (Small Business Innovative Research):***
<br>
The SBIR grant represents a lucrative opportunity for funding from the government. If Bio-Imaging secures this grant, they stand to gain $300,000 with the advantage of retaining full control over their business. However, the odds of winning this grant are higher with their 3D software success (70%) compared to their 2D version (20%).
<br><br>
***Nugrowth:***
<br>
Nugrowth Development offers an attractive proposition with a significant upfront investment of $1 million. This option could rapidly accelerate Bio-Imaging's development and market presence. However, it comes with the substantial trade-off of sharing 80% of their future profits, a decision that could have long-term financial implications.
<br><br>



### In selecting a programming language for constructing a decision tree, I choose R because of its robust capabilities in statistical analysis and its widespread use in the field of bioinformatics.

#### <br> [I will use DiagrammeR package to construct the decision tree]{style="color:orange"}

#### <br> I'll start by sketching out the entire narrative based on the summary page of our analysis. This will include incorporating the various scenarios proposed in the textbook. To ensure the plot is easy to grasp, I plan to first map out the overarching framework before delving into the specific possibilities associated with each node.

<br>

### Outline of Nodes for Bio-Imaging's Decision Tree

#### Starting Off:

-   **Option 1: Take Medtech's \$150K:** Bag the cash and end the story.

-   **Option 2: Pass on Medtech:** Keep the adventure going and develop further.

#### After Ditching Medtech:

-   **Event A: 3D Success (60% chance):** They totally nail the 3D software.

-   **Event B: 3D No-Go (40% chance):** Uh-oh, 3D software doesn’t pan out.

#### If 3D is a Hit:

-   **Choice C1: Aim for SBIR Grant:** Going for the big government grant.

-   **Choice C2: Say Yes to Nugrowth:** Dive into venture capital waters.

#### If 3D Tanks:

-   **Option D1: Throw in the Towel:** Call it quits, no more risks.

-   **Option D2: SBIR or Bust:** Still aim for the SBIR grant but with the 2D tech.

#### Chasing the SBIR Grant (After 3D Success):

-   **Event E1: SBIR Slip-Up (30% chance):** Miss the grant, lose \$200K.

-   **Event E2: SBIR Win (70% chance):** Score the grant and move forward.

#### Chasing the SBIR Grant (After 3D Flop):

-   **Event F1: SBIR Miss (80% chance):** No grant here either, down \$300K.

-   **Event F2: SBIR Score (20% chance):** Miracle win with the 2D project.

#### Rolling with SBIR Post-3D Triumph:

-   **Outcome G1: Big Bucks (20% chance):** Rake in \$280K.

-   **Outcome G2: Moderate Moola (40% chance):** Bag \$300K.

-   **Outcome G3: Tough Times (40% chance):** Ouch, down \$200K.

#### Taking the Nugrowth Plunge:

-   **Outcome H1: Jackpot (20% chance):** Cash in \$180K.

-   **Outcome H2: Decent Dough (40% chance):** Pocket \$400K.

-   **Outcome H3: Bummer (40% chance):** Lose \$200K.

#### After SBIR with 2D Tech:

-   **Outcome I1: 2D Success (25% chance):** Net \$120K.

-   **Outcome I2: 2D Downer (75% chance):** A loss of \$300K.
    <br><br>

### To begin with, I'll outline a summary of the story. This outline serves as a pivotal starting point for conducting our decision tree analysis. <br>

### Now, let's proceed to develop the decision tree. This approach will provide decision-makers with a clear visual representation, allowing them to see the 'forest' as a whole, rather than getting lost in the details of each 'tree'

<br><br>

```{r}
library(DiagrammeR)

grViz("
digraph BioImagingDecisionTree {

  graph [rankdir = LR]

  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica]

  # Define nodes
  Start [label = 'Start']
  Medtech [label = 'Take Medtech Offer - $150K']
  NoMedtech [label = 'Decline Medtech Offer']
  Success3D [label = '3D Success (60%)']
  Fail3D [label = '3D Failure (40%)']
  SBIR3D [label = 'Apply for SBIR (3D)']
  Nugrowth [label = 'Accept Nugrowth']
  Abandon [label = 'Abandon Project']
  SBIR2D [label = 'Apply for SBIR (2D)']
  SBIRSuccess3D [label = 'SBIR Success (3D)']
  SBIRFail3D [label = 'SBIR Failure (3D)']
  SBIRSuccess2D [label = 'SBIR Success (2D)']
  SBIRFail2D [label = 'SBIR Failure (2D)']
  HighProfitSBIR3D [label = 'High Profit SBIR (3D)']
  MediumProfitSBIR3D [label = 'Medium Profit SBIR (3D)']
  LowProfitSBIR3D [label = 'Low Profit SBIR (3D)']
  HighProfitSBIR2D [label = 'High Profit SBIR (2D)']
  LowProfitSBIR2D [label = 'Low Profit SBIR (2D)']
  HighProfitNugrowth [label = 'High Profit Nugrowth']
  MediumProfitNugrowth [label = 'Medium Profit Nugrowth']
  LowProfitNugrowth [label = 'Low Profit Nugrowth']

  # Define edges
  Start -> Medtech
  Start -> NoMedtech
  NoMedtech -> Success3D
  NoMedtech -> Fail3D
  Success3D -> SBIR3D
  Success3D -> Nugrowth
  Fail3D -> Abandon
  Fail3D -> SBIR2D
  SBIR3D -> SBIRSuccess3D
  SBIR3D -> SBIRFail3D
  SBIR2D -> SBIRSuccess2D
  SBIR2D -> SBIRFail2D
  SBIRSuccess3D -> HighProfitSBIR3D
  SBIRSuccess3D -> MediumProfitSBIR3D
  SBIRSuccess3D -> LowProfitSBIR3D
  SBIRSuccess2D -> HighProfitSBIR2D
  SBIRSuccess2D -> LowProfitSBIR2D
  Nugrowth -> HighProfitNugrowth
  Nugrowth -> MediumProfitNugrowth
  Nugrowth -> LowProfitNugrowth
}
", width = 1600, height = 800)

```

### Now, this is the very basic of descriptive decision tree. The manger would be able to capture the whole picture out of this tree, and make a decision based on the tree. However, this is not the end of the story. We can add some more information to this tree, such as the probabilities and the payoffs. Let's work on it.

<br><br>

```{r}
grViz("
digraph BioImagingDecisionTree {

  graph [rankdir = LR]
  
  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica]

  # Define nodes with probabilities and payoffs
  Start [label = 'Start']
  Medtech [label = 'Medtech Offer: $150K (100%)']
  NoMedtech [label = 'Decline Medtech Offer']
  Success3D [label = '3D Success (60%)']
  Fail3D [label = '3D Failure (40%)']
  SBIR3D [label = 'Apply for SBIR (3D)']
  Nugrowth [label = 'Accept Nugrowth']
  Abandon [label = 'Abandon Project (0)']
  SBIR2D [label = 'Apply for SBIR (2D)']
  SBIRSuccess3D [label = 'SBIR Success (70%)']
  SBIRFail3D [label = 'SBIR Failure (30%) - Loss $200K']
  SBIRSuccess2D [label = 'SBIR Success (20%)']
  SBIRFail2D [label = 'SBIR Failure (80%) - Loss $300K']
  HighProfitSBIR3D [label = 'High Profit: $2.8M (20%)']
  MediumProfitSBIR3D [label = 'Medium Profit: $300K (40%)']
  LowProfitSBIR3D [label = 'Low Profit: Loss $200K (40%)']
  HighProfitSBIR2D [label = 'High Profit: $1.2M (25%)']
  LowProfitSBIR2D [label = 'Low Profit: Loss $300K (75%)']
  HighProfitNugrowth [label = 'High Profit: $1.8M (20%)']
  MediumProfitNugrowth [label = 'Medium Profit: $400K (40%)']
  LowProfitNugrowth [label = 'Low Profit: Loss $200K (40%)']

  # Define edges
  Start -> Medtech
  Start -> NoMedtech
  NoMedtech -> Success3D
  NoMedtech -> Fail3D
  Success3D -> SBIR3D
  Success3D -> Nugrowth
  Fail3D -> Abandon
  Fail3D -> SBIR2D
  SBIR3D -> SBIRSuccess3D
  SBIR3D -> SBIRFail3D
  SBIR2D -> SBIRSuccess2D
  SBIR2D -> SBIRFail2D
  SBIRSuccess3D -> HighProfitSBIR3D
  SBIRSuccess3D -> MediumProfitSBIR3D
  SBIRSuccess3D -> LowProfitSBIR3D
  SBIRSuccess2D -> HighProfitSBIR2D
  SBIRSuccess2D -> LowProfitSBIR2D
  Nugrowth -> HighProfitNugrowth
  Nugrowth -> MediumProfitNugrowth
  Nugrowth -> LowProfitNugrowth
}
", width = 1600, height = 800)



```

### Now, we have the probabilities and the payoffs in the tree. The manager can make a decision based on the tree. However, the tree is still not complete. We can add some more information to the tree, such as the expected values and the expected utilities. Let's work on it.

```{r}
# Probabilities and Payoffs
p_success_3D <- 0.60
p_fail_3D <- 0.40
p_SBIR_success_3D <- 0.70
p_SBIR_fail_3D <- 0.30
p_SBIR_success_2D <- 0.20
p_SBIR_fail_2D <- 0.80

payoff_medtech <- 150000
payoff_SBIR_fail_3D <- -200000
payoff_SBIR_fail_2D <- -300000
payoff_high_profit_3D <- 2800000
payoff_medium_profit_3D <- 300000
payoff_low_profit_3D <- -200000
payoff_high_profit_2D <- 1200000
payoff_low_profit_2D <- -300000
payoff_high_profit_Nugrowth <- 1800000
payoff_medium_profit_Nugrowth <- 400000
payoff_low_profit_Nugrowth <- -200000

# Calculating Expected Values
EV_medtech <- payoff_medtech
EV_3D_success <- p_SBIR_success_3D * (payoff_high_profit_3D * 0.20 + payoff_medium_profit_3D * 0.40 + payoff_low_profit_3D * 0.40) +
                 p_SBIR_fail_3D * payoff_SBIR_fail_3D
EV_3D_fail <- p_SBIR_success_2D * (payoff_high_profit_2D * 0.25 + payoff_low_profit_2D * 0.75) +
              p_SBIR_fail_2D * payoff_SBIR_fail_2D
EV_Nugrowth <- payoff_high_profit_Nugrowth * 0.20 + payoff_medium_profit_Nugrowth * 0.40 + payoff_low_profit_Nugrowth * 0.40

# Printing Expected Values
print(paste("Expected Value if Medtech Offer is Accepted: $", EV_medtech))
print(paste("Expected Value if 3D is a Success: $", EV_3D_success))
print(paste("Expected Value if 3D Fails: $", EV_3D_fail))
print(paste("Expected Value if Nugrowth is Chosen: $", EV_Nugrowth))



```

<br><br>

### I'm using some probabilities and potential payoffs for each scenario. <br> It's a bit like weighing the odds and what they could win or lose in each case.<br><br>

### **Here's What I'm Considering:**

-   **Odds of 3D Development Going Well or Not:** 60% chance that the 3D project will be a success and a 40% chance it might not work out.

-   **Chances with the SBIR Grant:** They are to get a government grant (the SBIR) if they go with either the 3D or the 2D project.
    It's more likely to succeed with the 3D project.

-   **Money Matters:** They're looking at different money outcomes like getting \$150,000 from Medtech, what they might lose if the SBIR grant doesn't come through, and various profits (or losses) they could see from the 3D, 2D, and Nugrowth options.

### **Expected Values:**

#### I then do some math to figure out what I might expect to gain (or lose) on average from each decision. It's like looking at all possible outcomes, thinking about how likely each is, and then coming up with an average outcome.

1.  **Taking Medtech's Offer:** This one's a no-brainer; if they take their offer, they get \$150,000.

2.  **If 3D Works Out:** Here, I'm mixing the good and not-so-good financial outcomes based on whether they get the SBIR grant or not.

3.  **If 3D Doesn't Pan Out:** Doing similar math for the 2D project, but the odds aren't as great.

4.  **Going with Nugrowth:** Consider different profit scenarios with Nugrowth and see what the average outcome might look like.

### **Making Sense of It All:**

-   A high expected value means the decision could lead to good financial outcomes when you consider all the different ways things could go.

-   A lower expected value points to a decision being riskier or potentially less rewarding.

#### By figuring out these expected values, we're essentially trying to get a clearer picture of what each decision might bring financially. It helps us make smarter choices by understanding the risks and possible rewards involved.

#### 

#### Looking at the results below;

```         
[1] "Expected Value if Medtech Offer is Accepted: $ 150000"
[1] "Expected Value if 3D is a Success: $ 360000"
[1] "Expected Value if 3D Fails: $ -225000"
[1] "Expected Value if Nugrowth is Chosen: $ 440000"
```

Going with Nugrowth gives the most EV (Expected Value) in this scenario, meaning, you would [reject Medtech's \$150,000 offer]{style="color:red"}, and if 3D model developing is successful, you would [go with Nugrowth]{style="color:red"}.

<br><br>

```{r}
grViz("
digraph BioImagingDecisionTree {

  graph [rankdir = LR]
  
  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica]

  # Define nodes with probabilities and payoffs
  Start [label = 'Start']
  Medtech [label = 'Medtech Offer: $150K (100%)']
  NoMedtech [label = 'Decline Medtech Offer']
  Success3D [label = '3D Success (60%)']
  Fail3D [label = '3D Failure (40%)']
  SBIR3D [label = 'Apply for SBIR (3D)']
  Nugrowth [label = 'Accept Nugrowth']
  Abandon [label = 'Abandon Project (0)']
  SBIR2D [label = 'Apply for SBIR (2D)']
  SBIRSuccess3D [label = 'SBIR Success (70%)']
  SBIRFail3D [label = 'SBIR Failure (30%) - Loss $200K']
  SBIRSuccess2D [label = 'SBIR Success (20%)']
  SBIRFail2D [label = 'SBIR Failure (80%) - Loss $300K']
  HighProfitSBIR3D [label = 'High Profit: $2.8M (20%)']
  MediumProfitSBIR3D [label = 'Medium Profit: $300K (40%)']
  LowProfitSBIR3D [label = 'Low Profit: Loss $200K (40%)']
  HighProfitSBIR2D [label = 'High Profit: $1.2M (25%)']
  LowProfitSBIR2D [label = 'Low Profit: Loss $300K (75%)']
  HighProfitNugrowth [label = 'High Profit: $1.8M (20%)', shape = ellipse]
  MediumProfitNugrowth [label = 'Medium Profit: $400K (40%)', shape = ellipse]
  LowProfitNugrowth [label = 'Low Profit: Loss $200K (40%)', shape = ellipse]

  # Define edges
  Start -> Medtech
  Start -> NoMedtech [color=red, penwidth=2.0] 
  NoMedtech -> Success3D [color=red, penwidth=2.0] 
  NoMedtech -> Fail3D
  Success3D -> SBIR3D
  Success3D -> Nugrowth [color=red, penwidth=2.0] 
  Fail3D -> Abandon
  Fail3D -> SBIR2D
  SBIR3D -> SBIRSuccess3D
  SBIR3D -> SBIRFail3D
  SBIR2D -> SBIRSuccess2D
  SBIR2D -> SBIRFail2D
  SBIRSuccess3D -> HighProfitSBIR3D
  SBIRSuccess3D -> MediumProfitSBIR3D
  SBIRSuccess3D -> LowProfitSBIR3D
  SBIRSuccess2D -> HighProfitSBIR2D
  SBIRSuccess2D -> LowProfitSBIR2D
  Nugrowth -> HighProfitNugrowth [color=green, penwidth=2.0] 
  Nugrowth -> MediumProfitNugrowth [color=green, penwidth=2.0] 
  Nugrowth -> LowProfitNugrowth [color=green, penwidth=2.0] 
}
", width = 1600, height = 800)





```

### <br>But what happens if the development of the 3D Model falls through?<br>

### In such a scenario, it becomes crucial to identify the most advantageous course of action to take.<br>

```{r}
payoff_abandon <- -200000


# Calculating Expected Value for applying for SBIR with 2D technology
EV_SBIR_2D <- p_SBIR_success_2D * (payoff_high_profit_2D * 0.25 + payoff_low_profit_2D * 0.75) +
              p_SBIR_fail_2D * payoff_SBIR_fail_2D

# Print Expected Values
formatted_EV_abandon <- format(payoff_abandon, scientific = FALSE)
formatted_EV_SBIR_2D <- format(EV_SBIR_2D, scientific = FALSE)

print(paste("Expected Value if Abandoning the Project after Failing 3D: $", formatted_EV_abandon))
print(paste("Expected Value if Applying for SBIR with 2D Technology: $", formatted_EV_SBIR_2D))

```

### If the team fails to develop the 3D Model, opting to apply for the SBIR grant turns out to be the less favorable choice. This is because its expected value stands at a loss of -\$225,000, which is a greater loss compared to simply abandoning the project, which has an expected value of -\$200,000

<br><br>

### Now, let's finalize the decision tree by applying the expected value (EV) calculations based on the probabilities we've determined. What follows is an illustration where I'll highlight the paths, showcasing our findings from these calculations.

```{r}
grViz("
digraph BioImagingDecisionTree {

  graph [rankdir = LR]
  
  # Define node styles
  node [fontname = Helvetica, shape = box]
  edge [fontname = Helvetica, color=lightgray] 

  # Define nodes with probabilities and payoffs
  Start [label = 'Start']
  Medtech [label = 'Medtech Offer: $150K (100%)']
  NoMedtech [label = 'Decline Medtech Offer']
  Success3D [label = '3D Success (60%)']
  Fail3D [label = '3D Failure (40%)']
  SBIR3D [label = 'Apply for SBIR (3D)']
  Nugrowth [label = 'Accept Nugrowth']
  Abandon [label = 'Abandon Project (0)']
  SBIR2D [label = 'Apply for SBIR (2D)']
  SBIRSuccess3D [label = 'SBIR Success (70%)']
  SBIRFail3D [label = 'SBIR Failure (30%) - Loss $200K']
  SBIRSuccess2D [label = 'SBIR Success (20%)']
  SBIRFail2D [label = 'SBIR Failure (80%) - Loss $300K']
  HighProfitSBIR3D [label = 'High Profit: $2.8M (20%)']
  MediumProfitSBIR3D [label = 'Medium Profit: $300K (40%)']
  LowProfitSBIR3D [label = 'Low Profit: Loss $200K (40%)']
  HighProfitSBIR2D [label = 'High Profit: $1.2M (25%)']
  LowProfitSBIR2D [label = 'Low Profit: Loss $300K (75%)']
  HighProfitNugrowth [label = 'High Profit: $1.8M (20%)', shape = ellipse]
  MediumProfitNugrowth [label = 'Medium Profit: $400K (40%)', shape = ellipse]
  LowProfitNugrowth [label = 'Low Profit: Loss $200K (40%)', shape = ellipse]

  # Define edges with specific colors for highlighted paths
  Start -> Medtech
  Start -> NoMedtech [color=red, penwidth=2.0] 
  NoMedtech -> Success3D [color=red, penwidth=2.0] 
  NoMedtech -> Fail3D [color=blue, penwidth=2.0] 
  Success3D -> SBIR3D [color=lightgray, penwidth=1.0]
  Success3D -> Nugrowth [color=red, penwidth=2.0] 
  Fail3D -> Abandon [color=blue, penwidth=2.0] 
  Fail3D -> SBIR2D [color=lightgray, penwidth=1.0]
  SBIR3D -> SBIRSuccess3D [color=lightgray, penwidth=1.0]
  SBIR3D -> SBIRFail3D [color=lightgray, penwidth=1.0]
  SBIR2D -> SBIRSuccess2D [color=lightgray, penwidth=1.0]
  SBIR2D -> SBIRFail2D [color=lightgray, penwidth=1.0]
  SBIRSuccess3D -> HighProfitSBIR3D [color=lightgray, penwidth=1.0]
  SBIRSuccess3D -> MediumProfitSBIR3D [color=lightgray, penwidth=1.0]
  SBIRSuccess3D -> LowProfitSBIR3D [color=lightgray, penwidth=1.0]
  SBIRSuccess2D -> HighProfitSBIR2D [color=lightgray, penwidth=1.0]
  SBIRSuccess2D -> LowProfitSBIR2D [color=lightgray, penwidth=1.0]
  Nugrowth -> HighProfitNugrowth [color=green, penwidth=2.0] 
  Nugrowth -> MediumProfitNugrowth [color=green, penwidth=2.0] 
  Nugrowth -> LowProfitNugrowth [color=green, penwidth=2.0] 
}
", width = 1600, height = 800)


```

## <br>Conclusion

### In this Bio-Imaging's strategic choices, we've navigated a complex landscape of options and outcomes using decision tree analysis.

### Here's what we found out:

#### **- [Embracing Nugrowth]{style="color:red"}** If the 3D model is a hit, the smart move seems to be teaming up with Nugrowth. The expected value (EV) of this choice outshines the rest, promising the highest potential financial gain. It's a path lined with opportunity, albeit not without its risks.

#### **- The 3D Fails:** If the 3D model developing fails, abandoning the project is a less painful financial hit compared to chasing the SBIR grant with 2D technology.

#### **- The Medtech Offer:** While the immediate cash injection from Medtech is tempting, my analysis suggests that playing the long game might be more fruitful.

### Our decision tree, enhanced with probabilities, payoffs, expected values, and even color-coded for clarity, serves as a roadmap. It doesn't just tell us which path to choose; it shows us the landscape of possibilities, guiding Bio-Imaging's strategic decisions with a blend of data-driven insight and cautious optimism.

### In conclusion, Bio-Imaging stands at a crossroads, with each path leading to distinct futures. The choice isn't just about numbers; it's about weighing certainty against ambition, immediate gains against potential growth. It's a nuanced decision, and thanks to our analysis, it's one that can be made with both eyes wide open.

<br><br>

------------------------------------------------------------------------

------------------------------------------------------------------------

::: {#footer}
```{r echo=FALSE, results='asis'}
cat("Copyright © 2023-", format(Sys.Date(), "%Y"), "Sangho Lee, All rights reserved.")
```
:::
