---
title: "Bio-Imaging Development Strategies"
author: "Sangho Lee"
date: ' '
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: sentence
---

```{css, echo=FALSE}
body {
  font-family: 'Verdana', sans-serif;
}

#footer {
position: fixed;
left: 0;
bottom: 0;
width: 100%;
background-color: #f2f2f2; /* You can change the background color */
  color: black; /* Text color */
  text-align: center;
padding: 10px 0;
font-size: 1.2em;
}

```

------------------------------------------------------------------------

------------------------------------------------------------------------

### In selecting a programming language for constructing a decision tree, I choose R due to its robust capabilities in statistical analysis and its widespread use in the field of bioinformatics. I will use data.tree package to construct the decision tree unline the "Bill Sampras Summer Job" case which I used DiagreammeR package.

<br>

#### Let's get down to the work, before we actually start writing the tree nodes to make a decision, let's break down the whole story and see what the bio-(this company) is facing.

- Start: Root of the decision tree.
- Medtech Offer: Decide whether to accept Medtech's offer.
- Accept Medtech Offer: Bio-Imaging accepts the offer, and the process ends with the guaranteed amount.
- Decline Medtech Offer: Continue with the development to possibly get a better deal.
Development Success: Determine if the three-dimensional software development is successful.
Success: Successfully developed the 3D software.
Failure: Failed to develop the 3D software.
Funding Decision: If successful, decide the source of additional funding.
SBIR Grant: Apply for the SBIR grant.
Nugrowth Offer: Accept the Nugrowth Development offer.
SBIR Outcome: The outcome of the SBIR grant application.
Received: Grant is awarded.
Not Received: Grant is not awarded.
Market Success: The success of the product in the market.
High Profit
Medium Profit
Low Profit



```{r}
library(data.tree)

```

```{r}
# Define the tree structure
bioImagingDecisionTree <- Node$new("Start")
bioImagingDecisionTree$AddChild("Accept Medtech Offer")
developmentNode <- bioImagingDecisionTree$AddChild("Decline Medtech Offer")

successNode <- developmentNode$AddChild("Development Success")
failureNode <- developmentNode$AddChild("Development Failure")

successNode$AddChild("Apply for SBIR Grant")
nugrowthNode <- successNode$AddChild("Accept Nugrowth Offer")

nugrowthNode$AddChild("High Profit")
nugrowthNode$AddChild("Medium Profit")
nugrowthNode$AddChild("Low Profit")

failureNode$AddChild("Abandon Project")
failureNode$AddChild("Further Invest and Apply for SBIR Grant")

# Print the structure
print(bioImagingDecisionTree, "name")
plot(bioImagingDecisionTree)


```

------------------------------------------------------------------------

------------------------------------------------------------------------

::: {#footer}
```{r echo=FALSE, results='asis'}
cat("Copyright © 2023-", format(Sys.Date(), "%Y"), "Sangho Lee, All rights reserved.")
```
:::
